Source Summaries

### 2020-02-05 sourceSummaries.tex

    \title{Source Summaries}
    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
    Daniel Capps, Jacob Ruud}
    \date{\today}
    \maketitle
\break
\tableofcontents
\break

\noindent
\section{Security Analysis of Bluetooth Technology}

\noindent
\subsection{Citation}

@@

\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}

\noindent
\subsection{Group member}
Joshua Niemann
\subsection{Citation}

@@

\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}

\noindent
\subsection{Citation}

@@

\section{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}

\noindent
\subsection{Citation}

@@

\noindent
\section{Security Vulnerabilities in Bluetooth Technology as used in IoT}

\noindent
\subsection{Citation}

>>>>

    \title{Source Summaries}
    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
    Daniel Capps, Jacob Ruud}
    \date{\today}
    \maketitle
\break
\setcounter{tocdepth}{2}\tableofcontents
\break

\section{Week 3}

\noindent
\subsection{Security Analysis of Bluetooth Technology}

\subsubsection{Group Member}

\noindent
Quintin Walters

\noindent
\subsubsection{Citation}

@@

\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}

\noindent
\subsubsection{Group member}
Joshua Niemann

\subsubsection{Citation}

@@

\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}

\subsubsection{Group Member}

\noindent
Connor Leavesley

\noindent
\subsubsection{Citation}

@@

\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}

\subsubsection{Group Member}

\noindent
Connor Leavesley

\noindent
\subsubsection{Citation}

@@

\noindent
\subsection{Security Vulnerabilities in Bluetooth Technology as used in IoT}

\subsubsection{Group Member}

\noindent
Daniel Capps

\noindent
\subsubsection{Citation}
